A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with modeling and vis

## Time series visualization and models {#sec:ts-models}

As a special case of the data frame, a tsibble pipes into the grammar of graphics straight way, making most use of this powerful graphical system. It should be easy to create and extend some specialized time-related plotting methods based on tsibble structure, such as autocorrelation plots and calendar-based graphics [@wang-calendarviz-2018].

Modeling is crucial to explanatory and predictive analytics, but often imposes stricter assumptions on tsibble data. The verbs listed in Table \ref{tab:verb-table} ease the transition to a tsibble that suits modeling. A tidy forecasting framework built on top of tsibble is under development, which aims at promoting transparent forecasting practices and concise model representation. A tsibble usually contains multiple time series. Batch forecasting will be enabled if a univariate model, such as ARIMA and Exponential Smoothing, is applied to each time series independently. This yields a "mable" (short for model table), where each model only tags to each "key" value in tsibble to avoid expensive data copying and reduce model storage. The mable is further supplied to forecasting methods, to produce a tsibble in which each "key" along with its future time holds predictions. It also underlines the advantage of tsibble's "key" in linking between data inputs, models and forecasts. Advanced forecasting techniques, such as vector autocorrelation, hierarchical reconciliation, and ensembles, can be developed in alike spirit. The modeling module will be fulfilled and integrated eventually.

We go through the whole exploration circle, and keep iterating and refining until data insights gained. The tsibble data structure substantially lubricates between these modules for time-based pipelines. The cohesive and coherent framework results in more graceful and expressive code.

>>>>

## Time series visualization {#sec:ts-vis}

As a special case of the data frame, a tsibble pipes directly into the grammar of graphics. It is easy to create and extend specialist time-related plotting methods based on tsibble structure, such as autocorrelation plots and calendar-based graphics [@wang-calendarviz-2018].

## Time series models {#sec:ts-models}

Modeling is crucial to explanatory and predictive analytics, but often imposes stricter assumptions on tsibble data. The verbs listed in Table \ref{tab:verb-table} ease the transition to a tsibble that suits modeling. A tidy forecasting framework built on top of tsibble is under development, which aims at promoting transparent forecasting practices and concise model representation. A tsibble usually contains multiple time series. Batch forecasting will be enabled if a univariate model, such as ARIMA and Exponential Smoothing, is applied to each time series independently. This yields a "mable" (short for model table), where each model relates to each "key" value in tsibble. This avoids expensive data copying and reduces model storage. The mable is further supplied to forecasting methods, to produce a tsibble in which each "key" along with its future time holds predictions. It also underlines the advantage of tsibble's "key" in linking between data inputs, models and forecasts. Advanced forecasting techniques, such as vector autocorrelation, hierarchical reconciliation, and ensembles, can be developed in a similar spirit. The modeling module is a current endeavor.

<!--
We go through the whole exploration circle, and keep iterating and refining until data insights gained. The tsibble data structure substantially lubricates between these modules for time-based pipelines. The cohesive and coherent framework results in more graceful and expressive code.
-->
